The ChEMBL database as Linked Open Data

### 2012-05-01 article.tex
Removed a typo
Changed to the preferred reference
Consistent spelling of ChemSpider

In this study we extended Bioclipse DS with remote access to ChEMBL-RDF and Chemspider. 
This enables users browsing chemical structures in Bioclipse to look up near neighbors in Chemspider 
via the Chemspider Web API (SOAP), and for the found compounds to query ChEMBL-RDF for 
available interaction data. The results are presented alongside predictive models in Bioclipse (see Fig \ref{fig:bioclipse-ds}, and can be used for decision support when evaluating chemical structures and consider 
strategies for optimization.

\begin{figure*}[!ht]
		\begin{center}
		\includegraphics[width=16cm]{bioclipse-ds.png}
		\newline
		\caption[wee]{Screnshot from Bioclipse Decision Support with results from a Chsmpider + ChEMBL-RDF search. The top middle canvas contains the query structure, the top right canvas shows the near neighbors in Chemspider (via a similarStructure search), the lower right shows the chemical structure for the selected compound in the top right canvas, and the lower center canvas shows the found interactions for this compound.}
	\label{fig:bioclipse-ds}
		\end{center}
\end{figure*}

@@

Tim Hodson and Zach Beauvais of Kasabi and A. L\"ovgren at the at Uppsala Biomedical Centre at Uppsala University for their
support. OS acknowledges funding from the Swedish VR (2011-6129) and eSSENCE.

>>>>

In this study we extended Bioclipse DS with remote access to ChEMBL-RDF and ChemSpider. 
This enables users browsing chemical structures in Bioclipse to look up near neighbors in ChemSpider 
via the ChemSpider Web API (SOAP), and for the found compounds to query ChEMBL-RDF for 
available interaction data. The results are presented alongside predictive models in Bioclipse (see Fig \ref{fig:bioclipse-ds}, and can be used for decision support when evaluating chemical structures and consider 
strategies for optimization.

\begin{figure*}[!ht]
		\begin{center}
		\includegraphics[width=16cm]{bioclipse-ds.png}
		\newline
		\caption[wee]{Screnshot from Bioclipse Decision Support with results from a ChemSpider + ChEMBL-RDF search. The top middle canvas contains the query structure, the top right canvas shows the near neighbors in ChemSpider (via a similarStructure search), the lower right shows the chemical structure for the selected compound in the top right canvas, and the lower center canvas shows the found interactions for this compound.}
	\label{fig:bioclipse-ds}
		\end{center}
\end{figure*}

@@

Tim Hodson and Zach Beauvais of Kasabi and A. L\"ovgren at the BMC Computing Department at Uppsala University for their
support. OS acknowledges funding from the Swedish VR (2011-6129) and eSSENCE.
